3. Analysis Plan

### 2021-07-02 analysis/reports/rmd/03_dataAnalyses.Rmd
read & process broken data without risk info

stargazer(lm(formula = gender ~ treatment, data = covs),
          lm(formula = age ~ treatment, data = covs),
          lm(formula = switching_row ~ treatment, data = covs),
          lm(formula = donation ~ treatment, data = covs),

@@

olsStock1 <- lm(formula = stock ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 + 
                  pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                data = covariates[treatment == "replication"])
olsStock2  <- lm(formula = stock ~ gender + age + switching_row,
                data = covariates[treatment == "replication"])
olsGINI1  <- lm(formula = gini ~ gender + age + switching_row + pq01 + pq02 + pq03 + pq04 +
                  pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                data = covariates[treatment == "replication"])
olsGINI2  <- lm(formula = gini ~ gender + age + switching_row,
                data = covariates[treatment == "replication"])

>>>>

stargazer(lm(formula = gender ~ treatment, data = covs),
          lm(formula = age ~ treatment, data = covs),
          # lm(formula = switching_row ~ treatment, data = covs),
          lm(formula = donation ~ treatment, data = covs),

@@

olsStock1 <- lm(formula = stock ~ gender + age + 
                  # switching_row + 
                  pq01 + pq02 + pq03 + pq04 + 
                  pq05 + pq06 + pq07 +pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                data = covariates[treatment == "replication"])
olsStock2  <- lm(formula = stock ~ gender + age, # + switching_row,
                data = covariates[treatment == "replication"])
olsGINI1  <- lm(formula = gini ~ gender + age + 
                  # switching_row + 
                  pq01 + pq02 + pq03 + pq04 +
                  pq05 + pq06 + pq07 + pq08 + pq09 + pq10 + pq11 + pq12 + pq13 + pq14, 
                data = covariates[treatment == "replication"])
olsGINI2  <- lm(formula = gini ~ gender + age, # + switching_row,
                data = covariates[treatment == "replication"])
